---
layout: misc
title: Where are we?
output: md_document
---

```{r, setup, include=FALSE}
library(tidyverse)
library(readxl)
library(maps)
library(ggmap)
library(ggrepel)

key <- readLines("C:/Users/kcorreia/Dropbox (Amherst College)/Teaching/Spring 2020/Stat231/R Labs/apikey.txt")
register_google(key)
has_google_key()
```

# Where are we?

```{r, echo=FALSE}
# Get the world polygon
world <- map_data("world")

# get the data on where everyone is
where <- read.csv("C:/Users/kcorreia/Dropbox (Amherst College)/Teaching/Spring 2020/Stat231/Calendar Project/where.csv")

ggplot() +
  geom_polygon(data = world, aes(x=long, y = lat, group = group)
               , fill="grey", alpha=0.3) +
  #geom_point(data = where, aes(x=lon, y=lat, alpha=num)) +
  geom_text_repel(data = where %>% filter(place2 %in% c("Nairobi, Kenya"
                                                        , "New Dehli, India"))
                  , aes(x=lon, y=lat, label=place2)
                  , size=3) +
  geom_point(data = where, aes(x=lon, y=lat), color="#4A235A") +
  theme_void() + 
  #ylim(50,59) + 
  #coord_map() +
  theme(legend.position="none")

# third graphic 
usa <- map_data("usa") 

ggplot() + 
  geom_polygon(data = usa, aes(x=long, y = lat, group = group)
               , alpha = 0.3) + 
  coord_fixed(1.3) +
  geom_point(data = where %>% filter(place2 != "Nairobi, Kenya" &
                                       place2 != "New Dehli, India")
             , aes(x=lon, y=lat), color="#4A235A") +
 geom_text_repel(data = where %>% filter(place2 != "Nairobi, Kenya" &
                                       place2 != "New Dehli, India")
                  , aes(x=lon, y=lat, label=place2)
                  , size=3) +
  theme_void()

```


### What's the temperature where we are?  Using Google's BigQuery API

In one homework assignment, students connected to [Google's BigQuery API](https://cloud.google.com/bigquery/public-data "BigQuery Public Data") to access a public dataset containing weather information collected by NOAA.  They identified a weather station in the state or country in which they were currently residing, and plotted the average temperature by month in their location.  

Here is similar plot for the class, grouping by each of the different weather stations we searched. 

```{r, echo=FALSE, warning = FALSE, message = FALSE}
library(bigrquery)  
library(DBI)
options(gargle_quiet = FALSE)

bq_auth(path = "Stat231-Lab9b-Test-0d94d10c3b24.json")  
myproject <- "stat231-lab9b-test" 

Stat231_PS5_info <- read_excel("C:/Users/kcorreia/Dropbox (Amherst College)/Teaching/Spring 2020/Stat231/Calendar Project/Stat231_PS5_info.xlsx") 

stations <- Stat231_PS5_info %>%
  filter(is.na(Station_Number)==FALSE) %>%
  select(Station_Number)

# use the dbConnect command to establish the connection with Google's sample datasets
con <- dbConnect( 
  bigrquery::bigquery(),
  project = "publicdata",
  dataset = "samples",
  billing = myproject
)

#stations$Station_Number

# getting average temp by month for locations since 2000
query_stations <- bq_project_query(x = myproject
                    , query = "SELECT station_number, month
                                           , AVG(mean_temp) as avg_mean_temp
                                           , MIN(year) as first_year
                                           , MAX(year) as last_year
                               FROM `publicdata.samples.gsod` 
                               WHERE station_number IN (725060, 727730, 744910, 725033
                                                        , 722930, 720576, 994046, 744104
                                                        , 99406, 999999, 745090, 994046 
                                                        , 725080, 725035, 637410, 722789
                                                        , 724094, 724077, 997290, 726986)
                                              AND year > 2000
                               GROUP BY station_number, month
                               ORDER BY month")   

temperature_stations <- bq_table_download(query_stations)

# plotting average temp by month for the diff stations
ggplot(data = temperature_stations, aes(x = month, y = avg_mean_temp
                                        , group = as.factor(station_number)
                                        , color = as.factor(station_number))) +
  geom_line() + 
  geom_point() +
  labs(x="Month", y = "Average temperature (Fahrenheit)"
       , title = "Average temperature across our locations, 2000 - 2010") +
  scale_x_continuous(breaks=c(1:12)) +
  annotate("rect", xmin = 3.5, xmax = 5.3, ymin = 35, ymax = 85, alpha = .2) +
  geom_curve(x = 5, xend = 6, y = 40, yend = 42, color = "black"
             , arrow = arrow(length = unit(0.2,"cm")), curvature = 0) +
  annotate("text", size = 3, x = 7.2, y = 42, label = "The days should be \n getting warmer for most \n of us!") +
  theme(legend.position = "none")
```

```{r, include=FALSE}
temperature_stations %>% 
  filter(month==4) %>% 
  summarize(min = min(avg_mean_temp), max = max(avg_mean_temp)
            , median = median(avg_mean_temp))
```


Dear March - Come in  
by Emily Dickinson

Dear March - Come in -  
How glad I am -  
I hoped for you before -  
Put down your Hat -  
You must have walked -  
How out of Breath you are -  
Dear March, how are you, and the Rest -  
Did you leave Nature well -  
Oh March, Come right upstairs with me -  
I have so much to tell -
  
I got your Letter, and the Birds -  
The Maples never knew that you were coming -  
I declare - how Red their Faces grew -  
But March, forgive me -  
And all those Hills you left for me to Hue -  
There was no Purple suitable -  
You took it all with you -  
  
Who knocks? That April -  
Lock the Door -  
I will not be pursued -  
He stayed away a Year to call  
When I am occupied -  
But trifles look so trivial  
As soon as you have come  
  
That blame is just as dear as Praise  
And Praise as mere as Blame -  