---
layout: misc
title: Where are we?
output: md_document
---

```{r, setup, include=FALSE}
library(tidyverse)
```


```{r, include=FALSE}
library(bigrquery)  
library(DBI)
options(gargle_quiet = FALSE)

# change XXXX to the name of your json file that is stored in the same folder as this .Rmd file
bq_auth(path = "Stat231-Lab9b-Test-0d94d10c3b24.json")  

# change YYYY to your project id 
myproject <- "stat231-lab9b-test" 
```

# Where are we?

[[include map identifying where students are learning remotely]] \\

### What's the temperature where we are?  Using Google's BigQuery API

In one homework assignment, students connected to [Google's BigQuery API](https://cloud.google.com/bigquery/public-data "BigQuery Public Data") to access a public dataset containing weather information collected by NOAA.  They identified a weather station in the state or country in which they were currently residing, and plotted the average temperature by month in their location.

[[include figure that is overlays of students submission on temperature by month in their location from PS5]]
[[note the range in avg. temps for April/current month]]